Collaborative Visual Analysis with RCloud

### 2015-07-27 interviews.tex
s/coby/claude/g

Coby also works with text files and commands, rearranging source files
so active code is at the top. RCloud does not readily support this
workflow, so Coby often shares work by pasting code into an RCloud
notebook after he's done.

@@

Much of the time, commands typed at the R command line serve only a transitory
purpose, so having RCloud persist commands in cells can be annoying.
Coby notes, ``It saves everything I do like everything is gold, but most
of it is junk not meant to be saved.''

@@

The cell structure also can be problematic if some cells take a long time to
execute. High variance is common: cells may take anywhere from seconds to
hours to run. In this situation, the Run Whole Notebook button is dangerous.
Coby reports that when converting his work to notebooks, he
ends up with a lot of comments saying ``This cell takes a long time to run.''
To avoid this pitfall, some users write code to explicitly cache results.

>>>>

Claude also works with text files and commands, rearranging source files
so active code is at the top. RCloud does not readily support this
workflow, so Claude often shares work by pasting code into an RCloud
notebook after he's done.

@@

Much of the time, commands typed at the R command line serve only a transitory
purpose, so having RCloud persist commands in cells can be annoying.
Claude notes, ``It saves everything I do like everything is gold, but most
of it is junk not meant to be saved.''

@@

The cell structure also can be problematic if some cells take a long time to
execute. High variance is common: cells may take anywhere from seconds to
hours to run. In this situation, the Run Whole Notebook button is dangerous.
Claude reports that when converting his work to notebooks, he
ends up with a lot of comments saying ``This cell takes a long time to run.''
To avoid this pitfall, some users write code to explicitly cache results.
